\documentclass[10pt]{article}

\usepackage[T1]{fontenc}
\usepackage[letterpaper,margin=0.5in]{geometry}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}

\pagestyle{empty}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt}
\setlist[itemize]{leftmargin=1.15em,itemsep=0.08em,topsep=0.08em,parsep=0pt}

\newcommand{\resumeSection}[1]{
  \vspace{0.45em}
  {\large\bfseries #1}\par
  \vspace{0.12em}
  \hrule
  \vspace{0.28em}
}

\newcommand{\resumeRole}[4]{
  \textbf{#1} \hfill #4 \\
  \textit{#3} \hfill #2\par
  \vspace{0.02em}
}

\begin{document}

\begin{center}
{\LARGE\bfseries Dennis Zhou} \\
\vspace{0.2em}
US Citizen \\
\vspace{0.1em}
dennis@kernel.org $\bullet$ 651-442-8757 $\bullet$ San Francisco, CA
\end{center}

\resumeSection{Summary}
Staff software engineer with deep experience in Linux kernel, embedded systems,
distributed systems, and storage.
Focused on low-level systems, cross-stack debugging, and turning performance
and reliability problems into measurable, repeatable engineering work.

\vspace{0.28em}

Maintainer of the Linux kernel percpu memory allocator since v4.19 (09/2018).

\resumeSection{Experience}
\resumeRole{Cruise LLC}{04/2024 -- 09/2025}{Staff Software Engineer}{San Francisco, CA}
\textit{Senior Software Engineer II} \hfill 01/2023 -- 03/2024\par
\vspace{0.02em}
\begin{itemize}
\item Led reliability recovery for AIM, an audio and collision-detection
embedded system spanning FPGA and kernel; turned recurring test-vehicle
failures into a layer-by-layer investigation and hardening effort.
\item Reworked the debugging and recovery model with better logging,
bench-level reproduction, targeted instrumentation, and re-architected code
around coherent reset paths.
\item Championed hardware changes for audio and collision detection on the
future-generation program that simplified software and improved stability; the
design became plan of record.
\item Co-owned the Linux 5.4 to 5.15 upgrade across 10 devices on current and
next-generation vehicle platforms.
\item Built a Yocto shared-state cache on GCS with local artifact sync, cutting
clean build times from 90 minutes to 5 minutes.
\item Filesystems SME for Embedded Systems, debugging JFFS2/ext4 corruption and
eMMC/dm-verity boot failures; root-caused BSP-induced corruption, improved
userspace power-loss behavior, and upstreamed boot fixes.
\item Advised on IRQ steering and CPU pinning for Ray training jobs on a GCP H100
cluster, reducing host-workload contention.
\end{itemize}

\resumeRole{Snowflake Inc.}{10/2021 -- 01/2023}{Senior Software Engineer}{San Mateo, CA}
\begin{itemize}
\item Built a reproducible sandbox for the FoundationDB team to
standardize cluster setup, workloads, and metrics collection.
\item Integrated Prometheus and Grafana into the sandbox to
replace custom/ad hoc data analysis workflows and make observability data a first-class
citizen.
\item Contributed to Unistore storage and blob-management work.
\end{itemize}

\resumeRole{Google Inc.}{04/2020 -- 09/2021}{Software Engineer}{New York, NY}
\begin{itemize}
\item Contributed to I/O efficiency, thread scale-out, and
resource-accounting migration across the Colossus storage stack.
\item Built Runner, an internal framework for repeatable microsecond-level
benchmarking on the Colossus userspace client team.
\item Replaced a manual one-host-at-a-time workflow with parallelized
PR-based experiments, host-level reservations, and basic statistical analysis,
making large-scale performance testing practical.
\end{itemize}

\resumeRole{Facebook Inc.}{07/2018 -- 04/2020}{Software Engineer}{New York, NY}
\begin{itemize}
\item Linux kernel contributor across percpu memory allocation, cgroups, and
Btrfs; maintainer of the Linux percpu tree.
\item Developed Btrfs Async Discard to move SSD discard off the transaction
commit path, eliminating disk spikes that interfered with the main workload.
\item Implemented Btrfs Zstandard compression support.
\end{itemize}

\textit{Software Engineer Intern} \hfill 05/2017 -- 08/2017\par
\vspace{0.02em}
\begin{itemize}
\item Redesigned and upstreamed the Linux percpu allocator.
\item Replaced the prior area-map design with static bitmaps, cutting
worst-case free time by up to 68x.
\end{itemize}

\resumeSection{Education}
\textbf{University of Wisconsin}, Madison, WI \hfill 09/2016 -- 05/2018 \\
\textit{Master of Science}, Computer Sciences, Overall GPA: 4.0 \\
Advised by Professors Remzi and Andrea Arpaci-Dusseau

\vspace{0.18em}
\textbf{Georgia Institute of Technology}, Atlanta, GA \hfill 08/2011 -- 05/2014 \\
\textit{Bachelor of Science}, Computer Science, Major GPA: 4.0 \\
Threads: Information Internetworking and Systems \& Architecture

\resumeSection{Activities}
Enjoys outdoor activities including snowboarding, golf, climbing, and tennis. \\
RPM Raceway Jersey City, NJ -- \textbf{Fastest Lap Nov 2021}

\end{document}
